\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-07 ccs/eval.tex
pass over paper. added partitioning figure.

We next present \bonsai~\cite{bonsai} results on three
standard datasets: character recognition (Chars4k~\cite{campos},
accuracy 74.71\%), text recognition (USPS~\cite{hull}, accuracy
94.4\%), and object categorization (WARD~\cite{yang}, accuracy
95.7\%). 
The \bonsai models are already over integers and no porting from
floating-point is required.
We implement the trained classifiers in \tool for all the benchmarks
from~\cite{bonsai},
and show the representative results in Table~\ref{tab:bonsai}.
Out of all the benchmarks from~\cite{bonsai}, the dataset WARD
requires the largest model. 
The column ``depth''  shows the depth of the
tree used by \bonsai. The size of \tool 
program grows with the depth of the tree, as the straightforward \tool
implementation requires a loop for each layer of the
tree\footnote{We remark here that our current language does not support functions (which we leave for future work) and with this support, LOC would be lower and independent of depth.}.

@@

 \caption{Partitioning results for matrix factorization. The time reported by~\cite{valeriaMatrix} for this computation is 10440 seconds.}
 \label{tab:factor} 
\end{table}
Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth stage, which is the heaviest. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
%For this DNN, the specialized \minion protocol takes 544 seconds and
%communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to large
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion could run
out of memory but an appropriately partitioned \tool implementation would still
succeed. For example, consider a large DNN with $n$ layers such that the circuit for only a single layer can  fit into memory. Then, \tool using partitioning can evaluate this large DNN in $n$ stages.

>>>>

We next present \bonsai~\cite{bonsai} results on three
standard datasets: character recognition (Chars4k~\cite{campos},
accuracy 74.71\%), text recognition (USPS~\cite{hull}, accuracy
94.4\%), and object categorization (WARD\\~\cite{yang}, accuracy
95.7\%). 
The \bonsai models are already over integers and no porting from
floating-point is required.
We implement the trained classifiers in \tool for all the benchmarks
from~\cite{bonsai},
and show the representative results in Table~\ref{tab:bonsai}.
Out of all the benchmarks from~\cite{bonsai}, the dataset WARD
requires the largest model. 
The column ``depth''  shows the depth of the
tree used by \bonsai. The size of \tool 
program grows with the depth of the tree, as the straightforward \tool
implementation requires a loop for each layer of the
tree\footnote{We remark here that our current language does not support functions (which we leave for future work) and with this support, LOC would be lower and independent of depth.}.

@@

 \caption{Partitioning results for matrix factorization. The time reported by~\cite{valeriaMatrix} for this computation is 10440 seconds.}
 \label{tab:factor} 
\end{table}
Table~\ref{tab:cifar} shows the end-to-end numbers as
well as the numbers for the sixth stage, which is the heaviest. 
The number of gates are in millions, hence the suffix `m' in the last
three columns.
%For this DNN, the specialized \minion protocol takes 544 seconds and
%communicates 9272 Mb.
As with Table~\ref{tab:nn}, \tool generated generic 2PC protocol is
competitive with \minion here as well. Therefore,
we believe that with partitioning, \tool can scale to large
computations while maintaining performance
competitive with existing specialized protocols. In particular, for a
large enough DNN, \minion could run
out of memory but an appropriately partitioned \tool implementation would still
succeed. For example, consider a large DNN with $n$ layers such that the circuit for only a single layer can  fit into memory. Then, \tool using partitioning can evaluate this large DNN in $n$ stages. To further illustrate the need for and utility of partitioning, we ran a series of DNNs with different layers with and without partitioning (where partitioning was done for every layer of the DNN). For up to 5-layer DNNs, the performance of both settings was comparable, thereby illustrating that partitioning did not cause any overhead to performance. For networks that had 6 or more layers, performance of the protocol without partitioning dramatically dropped, while the protocol with partitioning continued to scale linearly. These results are illustrated in Figure~\ref{fig:partitioning}.

\begin{figure}
\includegraphics[width=8cm]{partitioning.png}
\caption{Comparison of \tool code with and without partitioning. x-axis denotes the number of layers of the DNN, while y-axis denotes time in seconds for the secure protocol.}
\label{fig:partitioning}
\end{figure}

### 2018-05-07 ccs/ex.tex
pass over paper. added partitioning figure.

The largest example benchmark in CBMC-GC is multiplication of two $8\times 8$ matrices for which it generates about a million gates and takes about ten seconds to run. In contrast, in \tool we use arithmetic sharing for this compute that generates <FILL> gates and completes in <FILL> seconds. We tried running CBMC-GC for multiplying two $20\times 20$ matrices and it timed out after 5 hours. In contrast, most of our benchmarks are much bigger. For example, we run the secure computation of a DNN for CIFAR-10 in 265 seconds which requires multiplying a $64\times576$ matrix with a $576\times1024$ matrix as a sub-computation. On the other hand, ObliVM scales to larger benchmarks with its use of Yao-pipelining \cite{yao-pipe}. We ran inner-product computations of varying lengths followed by a comparison in both ObliVM and \tool (see Table~\cite{oblivm-compare}). Our experiments show that we are atleast 30x faster than ObliVM due to our use of arithmetic sharing for inner-product computation.

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean ($\sim9x$ more time $\&$ $\sim20x$ more communication in a LAN setting). Since the performance gap between arithmetic and boolean multiplication is quite large, we believe that this choice is optimal for realistic network settings.
However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
We note that doing an optimal split between arithmetic and boolean is an NP-hard problem and in this work, we use some heuristics based on costs observed using microbenchmarking. 
For the smaller benchmarks of our evaluation, we wrote ABY code directly and the circuits
generated by our compiler had about the same size as the  hand written code. 
%Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

>>>>

The largest example benchmark in CBMC-GC is multiplication of two $8\times 8$ matrices for which it generates about a million gates and takes about ten seconds to run. In contrast, in \tool we use arithmetic sharing for this compute that generates 1218 gates and runs in about 0.1 seconds. We tried running CBMC-GC for multiplying two $20\times 20$ matrices and it timed out after 5 hours. In contrast, most of our benchmarks are much bigger. For example, we run the secure computation of a DNN for CIFAR-10 in 265 seconds which requires multiplying a $64\times576$ matrix with a $576\times1024$ matrix as a sub-computation. On the other hand, ObliVM scales to larger benchmarks with its use of Yao-pipelining \cite{yao-pipe}. We ran inner-product computations of varying lengths followed by a comparison in both ObliVM and \tool (see Table~\cite{oblivm-compare} in the Appendix). 
Our experiments show that we are atleast 30x faster than ObliVM due to our use of arithmetic sharing for inner-product computation.

\subsection{Cryptographic cost-aware compiler}
\label{sec:ccc}
One of the main challenges for our compiler is to split the compute between arithmetic and boolean parts well. 
As mentioned above, \tool is a cryptographic cost-aware compiler and uses the arithmetic and boolean costs of primitive operators and the inter-conversion costs to make the split. Cryptographic cost of converting an arithmetic share to a boolean share requires computing a garbled circuit for addition that is linear in size. Similarly, the cost of converting from boolean to arithmetic is computing a subtraction circuit inside garbled circuit that is again linear in size. ABY analyses all of these costs by running microbenchmarks for basic operations and interconversions (see Figures 2 and 3 in \cite{aby}). Based on these costs, our compiler has some hard constraints. For example, multiplication should always be performed in arithmetic circuit as the cost of boolean multiplication is much higher than  the cost of coercing from boolean to arithmetic, performing an arithmetic multiplication, and then coercing from arithmetic to boolean ($\sim9x$ more time $\&$ $\sim20x$ more communication in a LAN setting). Since the performance gap between arithmetic and boolean multiplication is quite large, we believe that this choice is optimal for realistic network settings.
However, this is not the case for addition. In \tool, if both the operands of addition are boolean shared, we do the addition using boolean circuit, else we use arithmetic circuit. Hence, addition may be done in arithmetic or boolean depending on the operands. 
Finally, all the boolean operations such as comparison, shifts, multiplexors, etc are done using Yao.
We note that doing an optimal split between arithmetic and boolean is an NP-hard problem and in this work, we use heuristics based on costs observed using microbenchmarking. 
For the smaller benchmarks of our evaluation, we wrote ABY code directly and the circuits
generated by our compiler had about the same size as the  hand written code. 
%Moreover, for our machine learning benchmarks (such as linear classifier, DNNs, etc) these choices seem optimal.

### 2018-05-07 ccs/impl.tex
pass over paper. added partitioning figure.

Since all these optimizations are standard compiler
optimizations~\cite{dragonbook}, we rely on their correctness to
maintain the correctness and security for the optimized programs.

>>>>

All these optimizations are standard compiler
optimizations~\cite{dragonbook}, and we rely on their correctness to
maintain the correctness and security for the optimized programs.

### 2018-05-07 ccs/intro.tex
pass over paper. added partitioning figure.

%Since its introduction in 1980s, there has been a long
%sequence of work that has transformed 2PC from a mere theoretical tool to
%something practically efficient and usable.
%Our goal is to build a framework that enables programmers, who are not
%experts in cryptography, to easily program efficient and scalable \mpc
%protocols. 
To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Suppose Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server classifier, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w$ and $x$. Alice has following options.

@@

\paragraph{Scalability (secure code partitioning).} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool.

@@

\paragraph{Related Work.}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty,autoS}). However, as Demmler et
al.~\cite{aby} observe, due
 to the high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. 
Additionally, these prior works provide informal languages
or libraries that lack formal semantics and static guarantees.
Finally, we focus on the language
features necessary to implement machine learning applications.
In particular, we do not discuss declassification of
intermediate values or indexing into arrays at secret indices.
 Handling them requires additional complexity. For example,
Wysteria~\cite{wysteria} handles the former using dependent types
and ObliVM~\cite{oblivm} uses Oblivious RAM for the latter.
These situations arise seldomly in the machine learning applications that we consider:
intermediate values don't need to be declassified and arrays are traversed in an oblivious manner.

%\dg{Cite works like Wysteria~\cite{wysteria} for public inputs and declassification of intermediate values, ObliVM~\cite{oblivm} for hiding secret array indices using Oblivious RAM. But since the focus of this work is machine learning applications, we do not concern ourselves with these language complexities.}
%Can be added to related work
% Kerschbaum et al.~\cite{autoS}
%provide a scheme to automatically assign homomorphic encryption or
%garbled circuits to each operators in a computation that has been expressed as a sequence of dyadic operations.
%They conjecture that the problem is NP hard and gave a linear programming based solution
%as well as a quadratic time greedy heuristic. \tool  uses a simpler constant time heuristic
%to assign arithmetic secret sharing or garbled circuits to sub-computations
%in a richer language with control flow statements such as loops and branches.
 We provide a detailed survey of related
work in \sectionref{related}.

>>>>

%Since its introduction in 1980s, there has been a long
%sequence of work that has transformed 2PC from a mere theoretical tool to
%something practically efficient and usable.
%Our goal is to build a framework that enables programmers, who are not
%experts in cryptography, to easily program efficient and scalable \mpc
%protocols. 
To understand the
state-of-the-art, let us consider an example underlying many
secure prediction algorithms. Suppose Alice wants to write
a \mpc protocol to securely
compute $w^Tx >b$. Here $w$ (a vector) and $b$ (a scalar) constitute
the server classifier, and $x$ is the client's input vector. Further,
$\cdot^{T}$ is the matrix transpose operator, and $w^Tx$ denotes the
inner product of  $w$ and $x$. Alice has the following options.

@@

\paragraph{Scalability (secure code partitioning).} \mpc tools
often do not scale to large functionalities. The reason is that
most \mpc implementations use a circuit-like representation as an
intermediate language. Hence, the largest compute that can be done
securely is upper-bounded by the largest circuit that can fit in the
machine memory\footnote{Using swap and
disk space is feasible but it causes huge slowdown.}. This is a
show-stopper for applications like secure machine learning, secure
prediction, etc. that operate on large amounts of data.
%\aseem{Can we
%cite something here to support this claim?}
\tool addresses the scalability concern using a novel technique that
we call secure code partitioning (or partitioning in short). At
a high level, we decompose the original program into a sequence of small
sub-programs, which are then sequentially processed by \tool, while
appropriately threading the intermediate outputs
along. While this
addresses the scalability concern (i.e., the circuit
sizes of the sub-programs are now small enough to fit in the memory),
we still have to address
the security risk of revealing the intermediate outputs. \tool comes
to the rescue; it automatically inserts the required instrumentation
to ensure security of these intermediate outputs (\sectionref{pipe}). As
we show in our
evaluation, partitioning allows us to program large applications
in \tool.

@@

\paragraph{Related Work.}
Before ABY~\cite{aby}, several works have proposed
combining secure computation protocols based on homomorphic
encryption and Yao's garbled circuits
(e.g. \cite{barni,blanton,brickell,franz,huang,valeriaMatrix,valeriaRidge,schropferK11}),
and some have also developed tools that allow writing such
combinations (e.g. \cite{bogdanov,lone,tasty,autoS}). However, as Demmler et
al.~\cite{aby} observe, due
 to the high conversion cost between
homomorphic encryption and Yao's garbled circuits, these combined
protocols do not gain much performance over a single
protocol. 
Additionally, these prior works provide informal languages
or libraries that lack formal semantics and static guarantees.
Finally, we focus on the language
features necessary to implement machine learning applications.
In particular, we do not discuss declassification of
intermediate values or indexing into arrays at secret indices.
 Handling them requires additional complexity. For example,
Wysteria~\cite{wysteria} handles the former using dependent types
and ObliVM~\cite{oblivm} uses Oblivious RAM for the latter.
These situations seldomly arise in the machine learning applications that we consider:
intermediate values don't need to be declassified and arrays are traversed in an oblivious manner. We provide a detailed survey of related
work in \sectionref{related}.

%\dg{Cite works like Wysteria~\cite{wysteria} for public inputs and declassification of intermediate values, ObliVM~\cite{oblivm} for hiding secret array indices using Oblivious RAM. But since the focus of this work is machine learning applications, we do not concern ourselves with these language complexities.}
%Can be added to related work
% Kerschbaum et al.~\cite{autoS}
%provide a scheme to automatically assign homomorphic encryption or
%garbled circuits to each operators in a computation that has been expressed as a sequence of dyadic operations.
%They conjecture that the problem is NP hard and gave a linear programming based solution
%as well as a quadratic time greedy heuristic. \tool  uses a simpler constant time heuristic
%to assign arithmetic secret sharing or garbled circuits to sub-computations
%in a richer language with control flow statements such as loops and branches.
